Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization

### 2024-03-20 manuscript.Rmd
add missing software to docker image

  \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
    {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
    {-1em}%
    {\normalfont\normalsize\bfseries\typesectitle}}
  \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
    {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
    {-\z@\relax}%
    {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
  \makeatother
repro:
  scripts:
    - R/plots.R
  files:
    - abstract.md
    - data/simulation.rds
  packages:
    - here
    - tidyverse
    - ggplot2
    - ggthemes
    - patchwork
    - tikzDevice
    - rticles
    - gert
    - aaronpeikert/repro@5075336
    - crsh/papaja@1c488f7
  tlmgr:
    - apa7
    - pgf
    - preview
  apt:
    - git
    - rsync
    - curl
    - inkscape
note: |
  The materials for this article are available on [GitHub](https://github.com/aaronpeikert/bayes-prereg) [@zenodo-release].
  This version was created from git commit ``r repro::current_hash(backend = "gert")``.
  The manuscript is available as [preprint](https://www.doi.org/10.31234/osf.io/cs8wb) [@peikertWhyDoesPreregistration2023].

>>>>

  \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
    {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
    {-1em}%
    {\normalfont\normalsize\bfseries\typesectitle}}
  \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
    {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
    {-\z@\relax}%
    {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
  \makeatother
repro:
  scripts:
    - R/plots.R
  files:
    - abstract.md
    - data/simulation.rds
  packages:
    - here
    - tidyverse
    - ggplot2
    - ggthemes
    - patchwork
    - tikzDevice
    - rticles
    - gert
    - aaronpeikert/repro@5075336
    - crsh/papaja@1c488f7
    - pacman
  tlmgr:
    - apa7
    - pgf
    - preview
    - scalerel
    - threeparttable
    - endfloat
    - was
    - multirow
    - threeparttablex
    - environ
    - trimspaces
    - xpatch
    - csquotes
  apt:
    - git
    - rsync
    - curl
    - inkscape
note: |
  The materials for this article are available on [GitHub](https://github.com/aaronpeikert/bayes-prereg) [@zenodo-release].
  This version was created from git commit ``r repro::current_hash(backend = "gert")``.
  The manuscript is available as [preprint](https://www.doi.org/10.31234/osf.io/cs8wb) [@peikertWhyDoesPreregistration2023].
